---
title: "535_final_Projcet"
author: "Group 6"
date: "3/29/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(gridExtra)
```

```{r}
#read csv file 
df = read.csv("vehicle-coupon-recommendation.csv")
```

```{r}
summary(df)

summarize_numeric = function(dataset) {
  
  dataset = select_if(dataset, is.numeric)
  summary.table = data.frame(Attribute = names(dataset))
  
  summary.table = summary.table %>% 
    mutate('Missing Values' = apply(dataset, 2, function (x) sum(x == "")),
           'Unique Values' = apply(dataset, 2, function (x) length(unique(x))),
           'Mean' = colMeans(dataset, na.rm = TRUE),
           'Min' = apply(dataset, 2, function (x) min(x, na.rm = TRUE)),
           'Max' = apply(dataset, 2, function (x) max(x, na.rm = TRUE)),
           'SD' = apply(dataset, 2, function (x) sd(x, na.rm = TRUE))
    )
  summary.table
}

summarize_numeric(df)
```

```{r}
summarize_character = function(dataset) {
  
  dataset = select_if(dataset, is.character)
  summary.table = data.frame(Attribute = names(dataset))
  summary.table = summary.table %>% 
    mutate('Missing Values' = apply(dataset, 2, function (x) sum(x == "")),
           'Unique Values' = apply(dataset, 2, function (x) length(unique(x))),
    )
  summary.table
}

summarize_character(df)

```

```{r}
# Missing value
df = df %>% select(-car)
df = df %>% filter(Bar != "", CoffeeHouse != "", CarryAway != "", RestaurantLessThan20 != "", Restaurant20To50 != "") 

#  Convert numeric attributes to factors
df$temperature = as.factor(df$temperature)
df$has_children = as.factor(df$has_children)
df$direction_same = as.factor(df$direction_same)

df = df %>% select(-direction_opp)

df$Y = as.factor(df$Y)

# Convert character attributes to factors
df = df %>% mutate(
  destination = as.factor(destination), 
  passanger = as.factor(passanger),
  weather = as.factor(weather),
  time = as.factor(time),
  coupon = as.factor(coupon),
  expiration = as.factor(expiration),
  gender = as.factor(gender),
  age = as.factor(age),
  maritalStatus = as.factor(maritalStatus),
  education = as.factor(education),
  occupation = as.factor(occupation),
  income = as.factor(income),
  Bar = as.factor(Bar),
  CoffeeHouse = as.factor(CoffeeHouse),
  CarryAway = as.factor(CarryAway),
  RestaurantLessThan20 = as.factor(RestaurantLessThan20),
  Restaurant20To50 = as.factor(Restaurant20To50),
)

summary(df)

df$time = factor(df$time, order = TRUE, levels = c("7AM", "10AM", "2PM","6PM","10PM"))
df$age = factor(df$age, order = TRUE, levels = c("below21","21", "26", "31","36","41","46","50plus"))
df$education = factor(df$education, order = TRUE, levels = c("Some High School","High School Graduate", "Some college - no degree", "Associates degree","Bachelors degree","Graduate degree (Masters or Doctorate)"))
df$income = factor(df$income, order = TRUE, levels = c("Less than $12500","$12500 - $24999","$25000 - $37499","$37500 - $49999","$50000 - $62499","$62500 - $74999", "$75000 - $87499", "$87500 - $99999","$100000 or More"))

df$Bar = factor(df$Bar, order = TRUE, levels = c("never","less1", "1~3", "4~8","gt8"))
df$CoffeeHouse = factor(df$CoffeeHouse, order = TRUE, levels = c("never","less1", "1~3", "4~8","gt8"))
df$CarryAway = factor(df$CarryAway, order = TRUE, levels = c("never","less1", "1~3", "4~8","gt8"))
df$RestaurantLessThan20 = factor(df$RestaurantLessThan20, order = TRUE, levels = c("never","less1", "1~3", "4~8","gt8"))
df$Restaurant20To50 = factor(df$Restaurant20To50, order = TRUE, levels = c("never","less1", "1~3", "4~8","gt8"))

summary(df)

df <- df %>%
  mutate('toCoupon_GEQ' = if_else(toCoupon_GEQ5min==1 & toCoupon_GEQ15min==0 & toCoupon_GEQ25min==0,'5-15', if_else(toCoupon_GEQ5min==1 & toCoupon_GEQ15min==1 & toCoupon_GEQ25min==0,'15-25','>25'))) %>%
  select(-toCoupon_GEQ5min,-toCoupon_GEQ15min,-toCoupon_GEQ25min)

df$toCoupon_GEQ = factor(df$toCoupon_GEQ, order = TRUE, levels = c("5-15", "15-25", ">25"))

summary(df)
```

```{r}
# Univariate analysis
# Create bar charts of factors

p1 = ggplot(df) + geom_bar(aes(x = destination))
p2 = ggplot(df) + geom_bar(aes(x = passanger))
p3 = ggplot(df) + geom_bar(aes(x = weather))
p4 = ggplot(df) + geom_bar(aes(x = temperature))
p5 = ggplot(df) + geom_bar(aes(x = time)) #QJH
p6 = ggplot(df) + geom_bar(aes(x = coupon))+ 
    theme(axis.text.x = element_text(angle = 90))
p7 = ggplot(df) + geom_bar(aes(x = expiration))
p8 = ggplot(df) + geom_bar(aes(x = gender))
p9 = ggplot(df) + geom_bar(aes(x = age))
p10 = ggplot(df) + geom_bar(aes(x = maritalStatus))+ 
    theme(axis.text.x = element_text(angle = 90)) #KYY
p11 = ggplot(df) + geom_bar(aes(x = has_children))
p12 = ggplot(df) + geom_bar(aes(x = education))+ 
    theme(axis.text.x = element_text(angle = 90))
p13 = ggplot(df) + geom_bar(aes(x = occupation)) + 
    theme(axis.text.x = element_text(angle = 90))
p14 = ggplot(df) + geom_bar(aes(x = income))+ 
    theme(axis.text.x = element_text(angle = 90))
p15 = ggplot(df) + geom_bar(aes(x = Bar))
p16 = ggplot(df) + geom_bar(aes(x = CoffeeHouse)) # FYF
p17 = ggplot(df) + geom_bar(aes(x = CarryAway))
p18 = ggplot(df) + geom_bar(aes(x = RestaurantLessThan20))
p19 = ggplot(df) + geom_bar(aes(x = Restaurant20To50))
p20 = ggplot(df) + geom_bar(aes(x = direction_same))
p21 = ggplot(df) + geom_bar(aes(x = Y))
p22 = ggplot(df) + geom_bar(aes(x = toCoupon_GEQ)) #ZAQ

grid.arrange(p1,p2,p3,p4,p5,p20,p22, nrow=3, top = "Contextual Factors")
grid.arrange(p6,p7,p21, nrow=1, top = "Coupon Factors and Outcome")
grid.arrange(p8,p9,p10,p11, nrow=2, top = "User Factors")
grid.arrange(p14,p15,p16,p17,p18,p19, nrow=2, top = "User Factors")
p12 #User
p13 #User


```

# Bivariate Analysis
Categories vs Categories

## coupon

```{r}
summary(df$coupon)
```

```{r}
ggplot(df) + geom_bar(aes(x=destination,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=passanger,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=weather,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=temperature,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=time,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=has_children,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=education,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=occupation,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=income,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Bar,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CarryAway,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=direction_same,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Y,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=toCoupon_GEQ,fill=coupon),position = "fill") + labs(y = "Percentage")
```

```{r}
library(lemon)
```

```{r}
p1 = grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=passanger,fill=coupon),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 30)),
  ggplot(df) + geom_bar(aes(x=time,fill=coupon),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 30)),
  ggplot(df) + geom_bar(aes(x=temperature,fill=coupon),position = "fill") + labs(y = "Percentage"),
  nrow = 1,ncol = 4,
  position = 'right'
)
#ggplot(df) + geom_bar(aes(x=expiration,fill=coupon),position = "fill") + labs(y = "Percentage")
p2 = grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=passanger,fill=expiration),position = "fill") + 
  labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 20)),
ggplot(df) + geom_bar(aes(x=time,fill=expiration),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 20)),
ggplot(df) + geom_bar(aes(x=temperature,fill=expiration),position = "fill") + 
  labs(y = "Percentage"),
  nrow = 1,ncol = 4,
  position = 'right'
)
grid.arrange(p1,p2,top = "Coupon Strategy under Different Circumstances")
```
### plot
```{r}
q1 = grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=gender,fill=coupon),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=age,fill=coupon),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 5)),
  ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=coupon),position = "fill") + labs(y = "Percentage"),
  nrow = 1,ncol = 3,position = 'right'
)
q2 = grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=gender,fill=expiration),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=age,fill=expiration),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 5)),
  ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=expiration),position = "fill") + labs(y = "Percentage"),
  nrow = 1,ncol = 3,position = 'right'
)
grid.arrange(q1,q2,top = "Coupon Strategy for Different Customers")
```


```{r}
p1 = ggplot(df) + geom_bar(aes(x=coupon,fill=destination),position = "fill") + labs(y = "Percentage") 
p2 =ggplot(df) + geom_bar(aes(x=coupon,fill=passanger),position = "fill") + labs(y = "Percentage")
p3 =ggplot(df) + geom_bar(aes(x=coupon,fill=weather),position = "fill") + labs(y = "Percentage")
p4 =ggplot(df) + geom_bar(aes(x=coupon,fill=temperature),position = "fill") + labs(y = "Percentage")
p5 =ggplot(df) + geom_bar(aes(x=coupon,fill=time),position = "fill") + labs(y = "Percentage")
p6 =ggplot(df) + geom_bar(aes(x=coupon,fill=expiration),position = "fill") + labs(y = "Percentage")
p7 =ggplot(df) + geom_bar(aes(x=coupon,fill=gender),position = "fill") + labs(y = "Percentage")
p8 =ggplot(df) + geom_bar(aes(x=coupon,fill=age),position = "fill") + labs(y = "Percentage")
p9 =ggplot(df) + geom_bar(aes(x=coupon,fill=maritalStatus),position = "fill") + labs(y = "Percentage")
p10 =ggplot(df) + geom_bar(aes(x=coupon,fill=has_children),position = "fill") + labs(y = "Percentage") + 
  theme(axis.text.x = element_text(angle = 30))
p11 =ggplot(df) + geom_bar(aes(x=coupon,fill=education),position = "fill") + labs(y = "Percentage") + 
  theme(axis.text.x = element_text(angle = 30))
p12 =ggplot(df) + geom_bar(aes(x=coupon,fill=occupation),position = "fill") + labs(y = "Percentage") + 
  theme(axis.text.x = element_text(angle = 30))
p13 =ggplot(df) + geom_bar(aes(x=coupon,fill=income),position = "fill") + labs(y = "Percentage") + 
  theme(axis.text.x = element_text(angle = 30))
p14 =ggplot(df) + geom_bar(aes(x=coupon,fill=Bar),position = "fill") + labs(y = "Percentage")
p15 =ggplot(df) + geom_bar(aes(x=coupon,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
p16 =ggplot(df) + geom_bar(aes(x=coupon,fill=CarryAway),position = "fill") + labs(y = "Percentage")
p17 =ggplot(df) + geom_bar(aes(x=coupon,fill=RestaurantLessThan20),position = "fill") + labs(y = "Percentage")
p18 =ggplot(df) + geom_bar(aes(x=coupon,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
p19 =ggplot(df) + geom_bar(aes(x=coupon,fill=direction_same),position = "fill") + labs(y = "Percentage")
p20 =ggplot(df) + geom_bar(aes(x=coupon,fill=Y),position = "fill") + labs(y = "Percentage")
p21 =ggplot(df) + geom_bar(aes(x=coupon,fill=toCoupon_GEQ),position = "fill") + labs(y = "Percentage")
```

```{r}
grid.arrange(p1,p2,p3,p4,p5,p6, nrow=3)
grid.arrange(p7,p8,p9,p10, nrow=2)
p11
p12
grid.arrange(p13,p14,p15,p16,p17, nrow=3)
grid.arrange(p18,p19,p20,p21, nrow=3)
```

Coupons of expensive restaurants are more likely to be delivered when the destination is home
Coupons of takeaways and more affordable restaurants are more likely to be accepted
Coupons of takeaways and more affordable restaurants are closer to the customers

## expiration

```{r}
summary(df$expiration)
```

```{r}
ggplot(df) + geom_bar(aes(x=destination,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=passanger,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=weather,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=temperature,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=time,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=coupon,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=has_children,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=education,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=occupation,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=income,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Bar,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CarryAway,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=expiration),position = "fill") +
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=direction_same,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Y,fill=expiration),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=toCoupon_GEQ,fill=expiration),position = "fill") +
  labs(y = "Percentage")
```

```{r}
ggplot(df) + geom_bar(aes(x=expiration,fill=destination),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=passanger),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=weather),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=temperature),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=time),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=gender),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=age),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=maritalStatus),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=has_children),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=education),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=occupation),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=income),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=Bar),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=CarryAway),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=RestaurantLessThan20),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=direction_same),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=Y),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=toCoupon_GEQ),position = "fill") + labs(y = "Percentage")
```

```{r}
grid.arrange(
ggplot(df) + geom_bar(aes(x=expiration,fill=temperature),position = "fill") + labs(y = "Percentage"),
ggplot(df) + geom_bar(aes(x=expiration,fill=coupon),position = "fill") + labs(y = "Percentage"),
ggplot(df) + geom_bar(aes(x=expiration,fill=Y),position = "fill") + labs(y = "Percentage"))
```
Coupons in hotter days expire earlier
Coupons of coffee house expire earlier
Coupons which expire later are more likely to be used

## gender

```{r}
summary(df$gender)
```

```{r}
ggplot(df) + geom_bar(aes(x=destination,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=passanger,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=weather,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=temperature,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=time,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=coupon,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=has_children,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=education,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=occupation,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=income,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Bar,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CarryAway,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=gender),position = "fill") +
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=direction_same,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Y,fill=gender),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=toCoupon_GEQ,fill=gender),position = "fill") +
  labs(y = "Percentage")
```

### plot
```{r}
grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=maritalStatus,fill=gender),position = "fill") + 
    labs(y = "Percentage") + theme(axis.text.x = element_text(angle = 10)),
  ggplot(df) + geom_bar(aes(x=has_children,fill=gender),position = "fill") + labs(y = "Percentage"),
  nrow = 1,ncol = 2
)
grid_arrange_shared_legend(
  ggplot(df) + geom_bar(aes(x=Bar,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=CarryAway,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=gender),position = "fill") +labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=Y,fill=gender),position = "fill") + labs(y = "Percentage"),
  nrow = 2,ncol = 3,top = "Lifestyle"
)
```

```{r}
ggplot(df) + geom_bar(aes(x=gender,fill=destination),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=passanger),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=weather),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=temperature),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=time),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=expiration),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=age),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=maritalStatus),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=has_children),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=education),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=occupation),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=income),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=Bar),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=CarryAway),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=RestaurantLessThan20),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=direction_same),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=Y),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=toCoupon_GEQ),position = "fill") + labs(y = "Percentage")
```
```{r}
grid.arrange(
  ggplot(df) + geom_bar(aes(x=gender,fill=maritalStatus),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=gender,fill=has_children),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=gender,fill=Bar),position = "fill") + labs(y = "Percentage")
)
```

Male are more likely to be unmarried
Male go to bars more frequently than female

## age

```{r}
summary(df$age)
```

```{r}
ggplot(df) + geom_bar(aes(x=destination,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=passanger,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=weather,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=temperature,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=time,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=coupon,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=has_children,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=education,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=occupation,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=income,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Bar,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CarryAway,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=age),position = "fill") +
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=direction_same,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Y,fill=age),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=toCoupon_GEQ,fill=age),position = "fill") +
  labs(y = "Percentage")
```
### plot

```{r}
ggplot(df) + geom_bar(aes(x=Bar,fill=age),position = "fill") + 
  labs(y = "Percentage")
```


```{r}
ggplot(df) + geom_bar(aes(x=age,fill=destination),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=passanger),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=weather),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=temperature),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=time),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=expiration),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=gender),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=maritalStatus),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=has_children),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=education),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=occupation),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=income),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=Bar),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=CarryAway),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=RestaurantLessThan20),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=direction_same),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=Y),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=toCoupon_GEQ),position = "fill") + labs(y = "Percentage")
```

```{r}
grid.arrange(
  ggplot(df) + geom_bar(aes(x=age,fill=Bar),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=age,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
)
```

People in their 20s go to bars more frequently
People below 21 go to coffee houses more frequently

## marital status

```{r}
summary(df$maritalStatus)
```

```{r}
ggplot(df) + geom_bar(aes(x=destination,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=passanger,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=weather,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=temperature,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=time,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=coupon,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=expiration,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=gender,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=age,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=has_children,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=education,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=occupation,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=income,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Bar,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CoffeeHouse,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=CarryAway,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=RestaurantLessThan20,fill=maritalStatus),position = "fill") +
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Restaurant20To50,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=direction_same,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=Y,fill=maritalStatus),position = "fill") + 
  labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=toCoupon_GEQ,fill=maritalStatus),position = "fill") +
  labs(y = "Percentage")
```

### plot

```{r}
grid.arrange(
  ggplot(df) + geom_bar(aes(x=Bar,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=Bar,fill=age),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=Bar,fill=maritalStatus),position = "fill") + labs(y = "Percentage")
)
```
```{r}
grid.arrange(
  ggplot(df) + geom_bar(aes(x=Y,fill=gender),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=Y,fill=age),position = "fill") + labs(y = "Percentage"),
  ncol = 2
  )
```



```{r}
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=destination),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=passanger),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=weather),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=temperature),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=time),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=coupon),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=expiration),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=gender),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=age),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=has_children),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=education),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=occupation),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=income),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=Bar),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=CarryAway),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=RestaurantLessThan20),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=direction_same),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=Y),position = "fill") + labs(y = "Percentage")
ggplot(df) + geom_bar(aes(x=maritalStatus,fill=toCoupon_GEQ),position = "fill") + labs(y = "Percentage")
```

```{r}
grid.arrange(
  ggplot(df) + geom_bar(aes(x=maritalStatus,fill=income),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=maritalStatus,fill=Bar),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=maritalStatus,fill=CoffeeHouse),position = "fill") + labs(y = "Percentage"),
  ggplot(df) + geom_bar(aes(x=maritalStatus,fill=Restaurant20To50),position = "fill") + labs(y = "Percentage")
)
```

People who are divorced or widowed tend to have lower income
People who are single or have unmarried partner go to bars more frequently
Widowed people barely go to coffee houses
Widowed people barely go to restaurants with higher price

# Hypothesis test

```{r}
help(table)
```

## coupon vs expiration

```{r}
table(df$coupon,df$expiration)
prop.table(table(df$coupon,df$expiration),1)
chisq.test(table(df$coupon,df$expiration),simulate.p.value = FALSE)
```

## coupon vs toCoupon_GEQ

```{r}
table(df$coupon,df$toCoupon_GEQ)
prop.table(table(df$coupon,df$toCoupon_GEQ),1)
chisq.test(table(df$coupon,df$toCoupon_GEQ),simulate.p.value = FALSE)
```

## temperature vs expiration

```{r}
table(df$temperature,df$expiration)
prop.table(table(df$temperature,df$expiration),1)
chisq.test(table(df$temperature,df$expiration),simulate.p.value = FALSE)
```

## destination vs expiration

```{r}
table(df$destination,df$expiration)
prop.table(table(df$destination,df$expiration),1)
chisq.test(table(df$destination,df$expiration),simulate.p.value = FALSE)
```

## weather vs expiration

```{r}
table(df$weather,df$expiration)
prop.table(table(df$weather,df$expiration),1)
chisq.test(table(df$weather,df$expiration),simulate.p.value = FALSE)
```

## gender vs maritalStatus

```{r}
table(df$gender,df$maritalStatus)
prop.table(table(df$gender,df$maritalStatus),1)
chisq.test(table(df$gender,df$maritalStatus),simulate.p.value = FALSE)
```

## gender vs Y

```{r}
table(df$gender,df$Y)
prop.table(table(df$gender,df$Y),1)
chisq.test(table(df$gender,df$Y),simulate.p.value = FALSE)
```

## gender vs has_children

```{r}
table(df$gender,df$has_children)
prop.table(table(df$gender,df$has_children),1)
chisq.test(table(df$gender,df$has_children),simulate.p.value = FALSE)
```

## gender vs bar

```{r}
table(df$gender,df$Bar)
prop.table(table(df$gender,df$Bar),1)
chisq.test(table(df$gender,df$Bar),simulate.p.value = FALSE)
```

## age vs bar

```{r}
table(df$age,df$Bar)
prop.table(table(df$age,df$Bar),1)
prop.table(table(df$age,df$Bar),2)
chisq.test(table(df$age,df$Bar),simulate.p.value = FALSE)
```

## age vs coffeehouse

```{r}
table(df$age,df$CoffeeHouse)
prop.table(table(df$age,df$CoffeeHouse),1)
chisq.test(table(df$age,df$CoffeeHouse),simulate.p.value = FALSE)
```

## maritalStatus vs income

```{r}
table(df$maritalStatus,df$income)
prop.table(table(df$maritalStatus,df$income),1)
chisq.test(table(df$maritalStatus,df$income),simulate.p.value = FALSE)
```

## maritalStatus vs bar

```{r}
table(df$maritalStatus,df$Bar)
prop.table(table(df$maritalStatus,df$Bar),1)
prop.table(table(df$maritalStatus,df$Bar),2)
chisq.test(table(df$maritalStatus,df$Bar),simulate.p.value = FALSE)
```

## maritalStatus vs coffeehouse

```{r}
table(df$maritalStatus,df$CoffeeHouse)
prop.table(table(df$maritalStatus,df$CoffeeHouse),1)
prop.table(table(df$maritalStatus,df$CoffeeHouse),2)
chisq.test(table(df$maritalStatus,df$CoffeeHouse),simulate.p.value = FALSE)
```

## maritalStatus vs restaurant<20

```{r}
table(df$maritalStatus,df$RestaurantLessThan20)
prop.table(table(df$maritalStatus,df$RestaurantLessThan20),1)
chisq.test(table(df$maritalStatus,df$RestaurantLessThan20),simulate.p.value = FALSE)
```

## maritalStatus vs restaurant20-50

```{r}
table(df$maritalStatus,df$Restaurant20To50)
prop.table(table(df$maritalStatus,df$Restaurant20To50),1)
chisq.test(table(df$maritalStatus,df$Restaurant20To50),simulate.p.value = FALSE)
```

## Cluster analysis

```{r}
df
```
```{r}
df %>% dplyr::select(Bar) %>% distinct()
```

```{r}
df_cluster = df
df_cluster <- df_cluster %>%
  mutate('education' = if_else(
    education == "Some High School" | education == "High School Graduate",'Low',
    if_else(education == "Some college - no degree" | education == "Associates degree",'Medium','High'))) 
df_cluster <- df_cluster %>% dplyr::select(-occupation)
df_cluster <- df_cluster %>%
  mutate('income' = if_else(
    income == "Less than $12500" | income == "$12500 - $24999" | income == "$25000 - $37499",'Low',
    if_else(income == "$37500 - $49999" | income == "$50000 - $62499" | income == "$62500 - $74999",'Medium','High'))) 
df_cluster <- df_cluster %>%
  mutate(passanger = if_else(
    passanger == "Alone",'Alone','Not alone'
  ))
df_cluster <- df_cluster %>%
  mutate(time = if_else(
    time == "7AM" | time == "10AM",'Morning',
    if_else(time == "2PM",'Noon','Evening'))) 
df_cluster <- df_cluster %>%
  mutate(age = if_else(
    age == "below 21" | age == "21" ,'Gen Z',
    if_else(age == "26" | age == "31" | age == "36"| age == "41",'Millennials','Gen X'))) 
df_cluster <- df_cluster %>%
  mutate(Bar = if_else(
    Bar == "never" | Bar == "less1" ,'barely','frequently')) 
df_cluster <- df_cluster %>%
  mutate(CoffeeHouse = if_else(
    CoffeeHouse == "never" | CoffeeHouse == "less1" ,'barely','frequently')) 
df_cluster <- df_cluster %>%
  mutate(CarryAway = if_else(
    CarryAway == "never" | CarryAway == "less1" ,'barely','frequently')) 
df_cluster <- df_cluster %>%
  mutate(RestaurantLessThan20 = if_else(
    RestaurantLessThan20 == "never" | RestaurantLessThan20 == "less1" ,'barely','frequently')) 
df_cluster <- df_cluster %>%
  mutate(Restaurant20To50 = if_else(
    Restaurant20To50 == "never" | Restaurant20To50 == "less1" ,'barely','frequently')) 
df_cluster
```

```{r}
library(klaR)
```

```{r}
set.seed(12)
df1 = df %>% dplyr::select(age,Bar,CarryAway,CoffeeHouse, education, gender, has_children, income, maritalStatus, Restaurant20To50, RestaurantLessThan20)
model = kmodes(df1,2,iter.max = 50)
model
model$size
```

```{r}
df$cluster = model$cluster
df
```

```{r}
df_1 = df %>% filter(cluster == 1)
df_2 = df %>% filter(cluster == 2)
```

```{r}
library(rpart)
library(rpart.plot)
```

```{r}
full_tree = rpart(Y~.,data = df,method = "class")
rpart.plot(full_tree,type = 5)
```
```{r}
full_tree1 = rpart(Y~.,data = df_1,method = "class")
rpart.plot(full_tree1,type = 5)
```
```{r}
full_tree2 = rpart(Y~.,data = df_2,method = "class")
rpart.plot(full_tree2,type = 5)
```



